---
title: "Untitled"
author: "Sheetal"
date: "3/3/2018"
output: html_document
---

Hi, I am sheetal. All my life only city has been my home that is Hyderbad. So i cant share list of homes. but i would share list of holiday places in last few years.

```{r setup, include=FALSE}
setwd("/Users/sheetalgolecha/Documents/Data collection/Session-4 Materials-20180221")
getwd()   # check if it worked

suppressPackageStartupMessages({
  if (!require(stringr)){ install.packages("stringr")}; library(stringr)
  if (!require(leaflet)){ install.packages("leaflet")}; library(leaflet)
  if (!require(jsonlite)){ install.packages("jsonlite")}; library(jsonlite)
  })
```
Lets load Json file. i have amended the file has the places i have been around where not present.

```{r}
 City_cords = jsonlite::fromJSON("./city.list.json") 
str(City_cords)

```
Now subsetting the whole list with only cities of india.
```{r}
a=City_cords$country=="IN"
ind_city=City_cords[a,]
```
I have visited a lot of places since my childhood, because my parents loved holiday. We had a lot of fun time.
	 But my real journey started in the year 2013, For the first time being in my home town I had to celebrate my birthday alone. I decided against it , and spent it with 20 strangers on a trek to Kalvantindurg and never realised when 20 strangers became friends and my journey to my discovery began. Since then treks have become my passion.

Next month I wen to Palani. (Its like heaven on earth) SO beautiful with all the huge trees around.
The journey continued to other places Salher(MAharahtra), Kodachadri(Karnataka) , rajmachi(Maharahtra) and so on.
I even did two Himalayan treks to Sandhakphu and goechala.

In middle of all this  my thirst for adventures dint end did my paragliding course in Kamshet.One heck of an experience.

With all the intro you might think I love Mountains but I love beaches too, So Goa is a place I visit at least once in 3 months for almost a year.

Lets look at my journey from 2013

Kalvantindurg (MH) (Mar 2015)
Palalni (TN) (Apr 2015)
Goa (Apr 2015)
Salher (Mh) (Jun 2015)
Raj Machi (Jul 2015)
Gokarna (KA) (Nov 2015)
Pallani (TN) (Nov 2015)
Sandhakphu (Sikkim) (Dec 2015)
Coorg (KA)(sep 2016)
Goechala (May 2017)
Rajgadh to Torna (Jun 2017)
Kerala (Oct 2017)
Goa (NOv 2017)

oops realised i have missed a lot of places nice way to update the sheet  :P.


```{r cars}
Places <- c("Hyderabad", "Prabhalgadh","Pallani","Salher","Rajmachi","Gokarna","Sandhakphu","Nagala","kamshet",                     "State of Goa","coorg","Goechala","State Of Kerala","Mumbai")

reason <- c("Home", "First Trek Mar 2013","Second trek Where i met an amazing person Mohit","another with old friends. where i realised am not peoples person","First with COusin bad idea :P","After a break of Six months :(","First Himalayan Trek","First Natural water slide","My first paralide :)","Love swimming and beach too","Famil trip2016","Second himalayan trek with a best friend touhing a height 5000 mtrs","Family trip 2017","Missed my friends")

```

now lets subset the places i have visited from Json file.

```{r }
my_list = data.frame(id=integer(), name=character(), country=character(),
                  coord.lon=numeric(), coord.lat=numeric(), stringsAsFactors=FALSE)
my_list

for(i in 1:length(Places)){
     x=ind_city[tolower(ind_city$name)==tolower(Places[i]),]
     my_list=rbind(my_list,x)
}

my_list  

```
Lets create a new dataframe where we have the cordinates and reason for my holidays.
```{r}
my_list

holiday=data.frame(Places,reason)
for (i in 1:length(Places)){
  holiday$lat[i]=my_list$coord$lat[i]
  holiday$lon[i]=my_list$coord$lon[i]
}
holiday
```
Lets create the max and min cordinates to know max size of the map.
```{r}
lon1=min(holiday$lon)-1;lon1
lon2=max(holiday$lon)+1;lon2
lat1=min(holiday$lat)-1;lat1
lat2=max(holiday$lat)+1;lat2
```
Lets view at my travel.
```{r}
mymap = leaflet() %>%
  
  addProviderTiles("Stamen.Watercolor") %>%    # try '?addProviderTiles'
  
  addProviderTiles("Stamen.TonerHybrid", 
                   options = providerTileOptions(opacity = 0.8)) %>%
  
  # setView(5, 20, zoom=1) %>%
  setMaxBounds(lon1, lat1, lon2, lat2) %>%
  
  # color and weight arguments for the color and weight of the line
  addPolylines(data=holiday, ~lon, ~lat, color = "BLACK", 
               weight = 2, opacity = 0.6) %>%
  
  addCircleMarkers(data=holiday, ~lon, ~lat,  color = "#daa520", 
                   opacity = 0.6, radius = 2, popup = paste(holiday$city, holiday$desc, sep="<br>"))

mymap
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



cya :)
